---
title: "Untitled"
author: "MyMac"
date: "2024-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
data <- read.csv("Obesity_CW.csv")

```


Attributes related with eating habits are:
Frequent consumption of high caloric food (FAVC),
Frequency of consumption of vegetables (FCVC),
Number of main meals (NCP),
Consumption of food between meals (CAEC),
Consumption of water daily (CH20),
and Consumption of alcohol (CALC).

Attributes related with the physical condition are:
Calories consumption monitoring (SCC),
Physical activity frequency (FAF),
Time using technology devices (TUE),
Transportation used (MTRANS),

Other variables were:
Gender, Age, Height and Weight.

Finally, all data was labeled and the class variable NObesity was created with the values of: Insufficient Weight, Normal Weight, Overweight Level I, Overweight Level II, Obesity Type I, Obesity Type II and Obesity Type III, based on Equation (1) and information from WHO and Mexican Normativity.